---
title: "pysty"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: true      
---

```{r, echo=FALSE}
rm(list=ls())
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
````

[![Build Status](https://travis-ci.org/trinker/pysty.svg?branch=master)](https://travis-ci.org/trinker/pysty)
[![Coverage Status](https://coveralls.io/repos/trinker/pysty/badge.svg?branch=master)](https://coveralls.io/r/trinker/pysty?branch=master)
`r verbadge`

**pysty** is a Python style packages importing using the common forms of: `import PACKAGE`, `import PACKAGE as ALIAS`, or `from PACKAGE import FUN1, FUN2, FUN_N`.  The latter even allows for importing non-exported functions into the global environment.  

This package is a proof of concept that such light weight importing and aliasing could be possible.  A user would use **pysty** because one wants to be explicit in all the functions used in a script as to what package they come from.  Aliasing package names is convenient for longer named packages.

# Installation

To download the development version of **pysty**:

Download the [zip ball](https://github.com/trinker/pysty/zipball/master) or [tar ball](https://github.com/trinker/pysty/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_gh("trinker/pysty")
```

# Contact

You are welcome to:    
- submit suggestions and bug-reports at: <https://github.com/trinker/pysty/issues>    
- send a pull request on: <https://github.com/trinker/pysty/>    
- compose a friendly e-mail to: <tyler.rinker@gmail.com>    

# Functions

There are only a few functions in the package: 

| Function                     |   Description                                      |
|------------------------------|--------------|-------------------------------------|
| `add_imports`                | Python style importing          |
| `clear_imports`              | Remove a named import(s) or all imports          |
| `get_imports`                | See imported packages          |
| `get_imports_functions`      | See imported functions          |



# Usage

```{r}
library(pysty)

add_imports('

import dplyr as dp
import ggplot2 as gg
import tidyr
from plyr import l_ply, rbind.fill

')

l_ply
dp::arrange
dp:::wrap
ls()

get_imports()
get_imports_functions()

clear_imports()
```

## It's all gone: Try it!

```r
l_ply
dp::arrange
dp:::wrap
ls()

get_imports()
get_imports_functions()
```
